% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\usepackage{fontspec}
\usepackage{polyglossia}
\setmainlanguage{arabic}
\newfontfamily\arabicfont[Script=Arabic, Path=/usr/share/fonts/truetype/amiri/, Extension=.ttf]{Amiri-Regular}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\author{}
\date{}
\begin{document}


\section{Arabic Fluency Roadmap: A Structured Guide to C1 in 8
Months}\label{arabic-fluency-roadmap-a-structured-guide-to-c1-in-8-months}

\textbf{(c) 2025 Liban Hussein}

\textbf{Ahlan}! This guide provides a detailed breakdown of the topics
and vocabulary you'll master to reach C1 proficiency---enabling fluency
in complex discussions, media analysis, and professional contexts.

I remember the first time I tried to speak Arabic outside the mosque- my
mind went completely blank. I could recite and undestand Qur'an, but
asking friends about a sports match they watched or discussing events in
Arabic? Total disaster. For years, I've been stuck in this weird middle
ground - classical texts make sense, but casual conversations feel like
running through quicksand. It's frustrating when your brain knows the
language but your mouth refuses to cooperate.

\textbf{Here's the truth I've learned:} Understanding Arabic and
speaking it fluently are two completely different skills. And I've
neglected the speaking part for too long. This guide is my public
commitment to change that. No more hiding behind passive understanding.
No more avoiding conversations. By \textbf{December 's end, 2025},
insha'Allah:

\textbf{My goals are to:}

\begin{itemize}
\tightlist
\item
  Speak spontaneously without mental translation
\item
  Conjugate verbs correctly in real-time conversations
\item
  Discuss complex topics beyond just religion
\item
  Translate short classical texts, including works and poems by Imām
  al-Shāfiʿī
  {[}\href{https://www.noor-book.com/en/ebook-\%D8\%AF\%D9\%8A\%D9\%88\%D8\%A7\%D9\%86-\%D8\%A7\%D9\%84\%D8\%A7\%D9\%85\%D8\%A7\%D9\%85-\%D8\%A7\%D9\%84\%D8\%B4\%D8\%A7\%D9\%81\%D8\%B9\%D9\%8A-pdf}{\textbf{Diwan
  al-Shāfiʿī}}{]}
\item
  Recite and understand portions of the Qur'an, ḥadīth, and duʿāʾ with
  insight into their grammar and rhetorical style
\item
  Write short essays and reflections in Arabic on Islamic and cultural
  topics
\item
  Participate in discussions and lessons conducted fully in Arabic
\item
  Finally feel confident calling myself fluent --- as a student of the
  language of the Qur'an
\end{itemize}

\textbf{This isn't about perfection. It's about bridging the gap between
what I understand and what I can express. That's the mission of the
Lisan Project.}

\textbf{What's Inside the Lisan Project Roadmap:}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Grammar Foundations}

  \begin{itemize}
  \tightlist
  \item
    Verb conjugations (past/present/command), noun gender/plural rules,
    sentence structures.
  \end{itemize}
\item
  \textbf{Core Vocabulary by Theme}

  \begin{itemize}
  \tightlist
  \item
    Daily life (family, work, travel), Islamic terms, media Arabic, and
    academic phrases.
  \end{itemize}
\item
  \textbf{Key Skills per Level}

  \begin{itemize}
  \tightlist
  \item
    \textbf{A1-A2:} Basic dialogues, introductions, and high-frequency
    verbs.
  \item
    \textbf{B1-B2:} Complex sentences, opinions, and cultural nuances.
  \item
    \textbf{C1 Mastery:} Critiquing texts, understanding dialects in
    media, and formal writing.
  \end{itemize}
\item
  \textbf{Thematic Chapters}

  \begin{itemize}
  \tightlist
  \item
    Household items, professions, health, holidays, etc.---each with
    targeted word lists.
  \end{itemize}
\end{enumerate}

\begin{tcolorbox}[enhanced jigsaw, coltitle=black, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{\textbf{Quote}}, leftrule=.75mm, colback=white, rightrule=.15mm, titlerule=0mm, opacitybacktitle=0.6, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, breakable, left=2mm, toptitle=1mm, bottomtitle=1mm, opacityback=0, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

\textbf{``العلم لا يُعطِيكَ بعضَهُ حتّى تُعطِيَهُ كلَّك، فإذا أعطَيتَهُ كلَّك، أعطاكَ
بعضَهُ''}

\emph{``Knowledge will not give you part of itself until you give it all
of yourself. And when you give it all of yourself, it will still only
give you part of itself.''}

\end{tcolorbox}




\end{document}
